Optimal management of a stochastically varying population when policy adjustment is costly

### 2013-11-07 inst/doc/policycosts/policycosts.Rnw
update figures (again)

\begin{figure}
<<Figure_1>>=
ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
@

@@

\begin{figure}
<<Figure_2, fig.width=12>>=
p2 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
  facet_grid(replicate~penalty_fn) + 
  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
p2
@
  \caption{Individual realizations of optimal harvesting strategy under the different functional forms of adjustment costs.}
\end{figure}

\begin{figure}
<<Figure_3, fig.width=12>>=
p1 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + 
  facet_grid(replicate~penalty_fn) + 
  labs(x="time", y="stock size", title = "Stock Dynamics")
p1
@
  \caption{Individual realizations of optimal stock size strategy under the different functional forms of adjustment costs.}
\end{figure}

@@

df3$reduction <- as.factor(df3$reduction)
ggplot(df3) + geom_line(aes(sigma_g, value, col=reduction, lty=variable)) + facet_wrap(~penalty_fn, scales="free_y") 
@
\end{figure}

>>>>

\begin{figure}
<<Figure_1>>=
ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()+theme_bw()
@

@@

\begin{figure}
<<Figure_2, fig.width=12>>=
p2 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
  facet_grid(replicate~penalty_fn) + 
  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
p2+theme_bw()
@
  \caption{Individual realizations of optimal harvesting strategy under the different functional forms of adjustment costs.}
\end{figure}

\begin{figure}
<<Figure_3, fig.width=12>>=
p1 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + 
  facet_grid(replicate~penalty_fn) + 
  labs(x="time", y="stock size", title = "Stock Dynamics")
p1+theme_bw()
@
  \caption{Individual realizations of optimal stock size strategy under the different functional forms of adjustment costs.}
\end{figure}

@@

df3$reduction <- as.factor(df3$reduction)
ggplot(df3) + geom_line(aes(sigma_g, value, col=reduction, lty=variable)) + facet_wrap(~penalty_fn, scales="free_y", ncol=1) 
@
\end{figure}

### 2013-11-07 inst/doc/policycosts/policycosts.tex
update figures (again)

\begin{document}

@@

\begin{table}[ht]
\centering
\begin{tabular}{rlrrrrrr}
  \hline
 & penalty\_fn & ignore\_cost & ignore\_fraction & assume\_cost & assume\_fraction & sigma\_g & reduction \\ 
  \hline
1 & L1 & 14536.09 & 1.00 & 16857.61 & 1.00 & 0.05 & 0.10 \\ 
  2 & L2 & 11020.10 & 0.76 & 15538.44 & 0.92 & 0.05 & 0.10 \\ 
  3 & fixed & 13584.97 & 0.92 & 17582.78 & 1.05 & 0.05 & 0.10 \\ 
  4 & L1 & 9273.66 & 1.09 & 17561.81 & 1.04 & 0.05 & 0.20 \\ 
  5 & L2 & 11020.10 & 0.76 & 15538.44 & 0.92 & 0.05 & 0.20 \\ 
  6 & fixed & 8332.45 & 0.84 & 17401.82 & 1.03 & 0.05 & 0.20 \\ 
  7 & L1 & -641.78 & 0.21 & 15451.25 & 0.92 & 0.05 & 0.30 \\ 
  8 & L2 & -272586.11 & -24.90 & 11567.12 & 0.69 & 0.05 & 0.30 \\ 
  9 & fixed & -1213.01 & -0.46 & 15519.95 & 0.92 & 0.05 & 0.30 \\ 
  10 & L1 & 18281.97 & 1.01 & 20973.56 & 0.99 & 0.20 & 0.10 \\ 
  11 & L2 & 12462.51 & 0.72 & 19392.85 & 0.91 & 0.20 & 0.10 \\ 
  12 & fixed & 16691.94 & 1.03 & 20143.80 & 0.95 & 0.20 & 0.10 \\ 
  13 & L1 & 12788.95 & 0.96 & 20663.21 & 0.97 & 0.20 & 0.20 \\ 
  14 & L2 & 12462.51 & 0.72 & 19392.85 & 0.91 & 0.20 & 0.20 \\ 
  15 & fixed & 12399.01 & 0.88 & 21289.21 & 1.00 & 0.20 & 0.20 \\ 
  16 & L1 & 9099.48 & 0.73 & 19999.07 & 0.94 & 0.20 & 0.30 \\ 
  17 & L2 & -6337.76 & -0.39 & 17765.33 & 0.83 & 0.20 & 0.30 \\ 
  18 & fixed & 7399.01 & 0.62 & 21969.84 & 1.03 & 0.20 & 0.30 \\ 
  19 & L1 & 30227.43 & 1.07 & 31377.07 & 0.94 & 0.50 & 0.10 \\ 
  20 & L2 & 33472.18 & 1.00 & 33472.18 & 1.00 & 0.50 & 0.10 \\ 
  21 & fixed & 28926.73 & 1.09 & 30500.85 & 0.91 & 0.50 & 0.10 \\ 
  22 & L1 & 24157.93 & 1.10 & 31767.92 & 0.95 & 0.50 & 0.20 \\ 
  23 & L2 & 19091.31 & 0.93 & 29225.46 & 0.87 & 0.50 & 0.20 \\ 
  24 & fixed & 23573.19 & 1.02 & 30069.80 & 0.90 & 0.50 & 0.20 \\ 
  25 & L1 & 21086.12 & 1.12 & 32035.93 & 0.96 & 0.50 & 0.30 \\ 
  26 & L2 & 19091.31 & 0.93 & 29225.46 & 0.87 & 0.50 & 0.30 \\ 
  27 & fixed & 17209.56 & 0.85 & 32946.24 & 0.98 & 0.50 & 0.30 \\ 
   \hline
\end{tabular}

\caption{Overall cost of assuming policy adjustment costs apply when they are absent (first value) or from ignoring them when they are present (second value). These overall costs are shown for different severities of policy adjustment costs (columns) and levels of environmental variability (rows) and for three different functional forms for policy adjustment costs ($\Pi_i$ for $ i=1-3$). Values expressed as percentages of the maximum expected net present value when no policy adjustment costs apply and this is known to managers ($ NPV_0 ({\bf h_0^*}) $). }
\end{table}

>>>>

\begin{document}
%\SweaveOpts{concordance=TRUE, echo=FALSE}

@@

% latex table generated in R 3.0.2 by xtable 1.7-1 package
% Wed Nov  6 20:50:41 2013
\begin{table}[ht]
\centering
\begin{tabular}{rlrrrrrr}
  \hline
 & penalty\_fn & ignore\_cost & ignore\_fraction & assume\_cost & assume\_fraction & sigma\_g & reduction \\ 
  \hline
1 & L1 & 14536.09 & 1.00 & 16857.61 & 1.00 & 0.05 & 0.10 \\ 
  2 & L2 & 11020.10 & 0.76 & 15538.44 & 0.92 & 0.05 & 0.10 \\ 
  3 & fixed & 13584.97 & 0.92 & 17582.78 & 1.05 & 0.05 & 0.10 \\ 
  4 & L1 & 9273.66 & 1.09 & 17561.81 & 1.04 & 0.05 & 0.20 \\ 
  5 & L2 & 11020.10 & 0.76 & 15538.44 & 0.92 & 0.05 & 0.20 \\ 
  6 & fixed & 8332.45 & 0.84 & 17401.82 & 1.03 & 0.05 & 0.20 \\ 
  7 & L1 & -641.78 & 0.21 & 15451.25 & 0.92 & 0.05 & 0.30 \\ 
  8 & L2 & -272586.11 & -24.90 & 11567.12 & 0.69 & 0.05 & 0.30 \\ 
  9 & fixed & -1213.01 & -0.46 & 15519.95 & 0.92 & 0.05 & 0.30 \\ 
  10 & L1 & 18281.97 & 1.01 & 20973.56 & 0.99 & 0.20 & 0.10 \\ 
  11 & L2 & 12462.51 & 0.72 & 19392.85 & 0.91 & 0.20 & 0.10 \\ 
  12 & fixed & 16691.94 & 1.03 & 20143.80 & 0.95 & 0.20 & 0.10 \\ 
  13 & L1 & 12788.95 & 0.96 & 20663.21 & 0.97 & 0.20 & 0.20 \\ 
  14 & L2 & 12462.51 & 0.72 & 19392.85 & 0.91 & 0.20 & 0.20 \\ 
  15 & fixed & 12399.01 & 0.88 & 21289.21 & 1.00 & 0.20 & 0.20 \\ 
  16 & L1 & 9099.48 & 0.73 & 19999.07 & 0.94 & 0.20 & 0.30 \\ 
  17 & L2 & -6337.76 & -0.39 & 17765.33 & 0.83 & 0.20 & 0.30 \\ 
  18 & fixed & 7399.01 & 0.62 & 21969.84 & 1.03 & 0.20 & 0.30 \\ 
  19 & L1 & 30227.43 & 1.07 & 31377.07 & 0.94 & 0.50 & 0.10 \\ 
  20 & L2 & 33472.18 & 1.00 & 33472.18 & 1.00 & 0.50 & 0.10 \\ 
  21 & fixed & 28926.73 & 1.09 & 30500.85 & 0.91 & 0.50 & 0.10 \\ 
  22 & L1 & 24157.93 & 1.10 & 31767.92 & 0.95 & 0.50 & 0.20 \\ 
  23 & L2 & 19091.31 & 0.93 & 29225.46 & 0.87 & 0.50 & 0.20 \\ 
  24 & fixed & 23573.19 & 1.02 & 30069.80 & 0.90 & 0.50 & 0.20 \\ 
  25 & L1 & 21086.12 & 1.12 & 32035.93 & 0.96 & 0.50 & 0.30 \\ 
  26 & L2 & 19091.31 & 0.93 & 29225.46 & 0.87 & 0.50 & 0.30 \\ 
  27 & fixed & 17209.56 & 0.85 & 32946.24 & 0.98 & 0.50 & 0.30 \\ 
   \hline
\end{tabular}
\end{table}

Overall cost of assuming policy adjustment costs apply when they are absent (first value) or from ignoring them when they are present (second value). These overall costs are shown for different severities of policy adjustment costs (columns) and levels of environmental variability (rows) and for three different functional forms for policy adjustment costs ($\Pi_i$ for $ i=1-3$). Values expressed as percentages of the maximum expected net present value when no policy adjustment costs apply and this is known to managers ($ NPV_0 ({\bf h_0^*}) $).
